### 2016-06-16 capability-machine.tex
added comment question about continuation predicate
added another comment question about continuation predicate

Now we need to jump to $\malloc$, so we need to make sure that the precondition in the specification is satisfied. To do this, we first need a world that models the part of the heap that is currently in use which is $\hs$. We pick the world $W$ to be:
\begin{align*}
  W(\codelabel{adv}) & = \iota_{\var{adv},\var{advend}} \\
  W(\init)           & = \iota_{\init,\init+\var{proglen} - 1} \\
  W(\rio)            & = \lambda W\ldotp \{(n,\hs) \mid \hs(0) = -1 \text{ or } \\
                     &   \hphantom{ = \lambda W\ldotp \{(n,\hs) \mid }\:\; \hs(0) \text{ even and positive} \}
\end{align*}
for all other addresses $a$ that are not captured in the above but are part of $hs$, we define a new region $r$ in $W$ where
\begin{align*}
  W(r) & = \iota_{a,a}
\end{align*}
Then we need to argue that $\heapSat{\hs}{n-i}{W}$. Given any address, in $\hs$ there is a region that covers that address, and the regions cover only the addresses in $\hs$. Now each of the heap segments have to be accepted by the respective regions. For the adversary, we assumed that it had no capabilities, so all the addresses contain intergers which i trivially in the value relation. The same goes for the heap segment with the ticket dispenser test program and the remaining addresses of the heap but addresses 0 \lau{need assumption about this.} The io address contains $-1$ at this point of the execution which mean that the heapsegment only consisting of address 0 is accepted in this world.

@@

``Continuation'' relation:
\begin{align*}
  \stdkr \quad : & \quad  \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stdkr(W) \defeq & \{ \npair{c} \mid \\
                   & \quad \forall v \in \stdvr(W)\ldotp \\
                   & \qquad  \forall W' \future W\ldotp %on the whiteboard, we had public future world.
                     \forall \heapSat{n'}{W'} \ldotp \forall \reg \in \stdrr(W') \\
                   & \qquad \quad (n,reg\update{r_0}{v}\update{\pcreg}{\updatePcPerm{c}}, \heap) \in \observations(W) \}
\end{align*}
``Expression'' relation:
\begin{align*}
  \stder \quad : & \quad \Worlds \monfun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder(W) \defeq & \{ \npair{\pc} \mid \\
                   & \quad \forall \reg \in \stdrr(W) \ldotp \\
                   & \qquad \forall \npair{c} \in \stdkr(W) \ldotp \\
                   & \qquad \quad  \forall \heapSat{n}{W}, \heap_f \ldotp \\
                   & \qquad \qquad (n,\reg\update{r_0}{c}\update{\pcreg}{\pc},\heap \uplus \heap_f) \in \observations(W) \}
\end{align*}

>>>>

Now we need to jump to $\malloc$, so we need to make sure that the precondition in the specification is satisfied. To do this, we first need a world that models the part of the heap that is currently in use which is $\hs$. We pick the world $W$ to be:
\begin{align*}
  W(\codelabel{adv}) & = \iota_{\var{adv},\var{advend}} \\
  W(\init)           & = \iota_{\init,\init+\var{proglen} - 1} \\
  W(\rio)            & = \lambda W\ldotp \{(n,\hs) \mid \hs(0) = -1 \text{ or } \\
                     &   \hphantom{ = \lambda W\ldotp \{(n,\hs) \mid }\:\; \hs(0) \text{ even and positive} \}
\end{align*}
for all other addresses $a$ that are not captured in the above but are part of $hs$, we define a new region $r$ in $W$ where
\begin{align*}
  W(r) & = \iota_{a,a}
\end{align*}
Then we need to argue that $\heapSat[\hs]{n-i}{W}$. Given any address, in $\hs$ there is a region that covers that address, and the regions cover only the addresses in $\hs$. Now each of the heap segments have to be accepted by the respective regions. For the adversary, we assumed that it had no capabilities, so all the addresses contain intergers which i trivially in the value relation. The same goes for the heap segment with the ticket dispenser test program and the remaining addresses of the heap but addresses 0 \lau{need assumption about this.} The io address contains $-1$ at this point of the execution which mean that the heapsegment only consisting of address 0 is accepted in this world.

@@

``Continuation'' relation:
\begin{align*}
  \stdkr \quad : & \quad  \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stdkr(W) \defeq & \{ \npair{c} \mid \\
                   & \quad \forall v \in \stdvr(W)\ldotp \\
                   & \qquad  \forall W' \future W\ldotp %on the whiteboard, we had public future world.
                     \forall \heapSat{n'}{W'} \ldotp \forall \reg \in \stdrr(W') \\
                   & \qquad \quad (n,reg\update{r_0}{v}\update{\pcreg}{\updatePcPerm{c}}, \heap) \in \observations(W) \}
\end{align*}
\lau{$r_1$ contains the ``return value'', shouldn't that be the one we quantify over?} \\
\lau{When continuation is invoked, it has to be in registers, but here we do not require it to be in the value relation, so it seems impossible to show some of the required conditions.}
``Expression'' relation:
\begin{align*}
  \stder \quad : & \quad \Worlds \monfun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder(W) \defeq & \{ \npair{\pc} \mid \\
                   & \quad \forall \reg \in \stdrr(W) \ldotp \\
                   & \qquad \forall \npair{c} \in \stdkr(W) \ldotp \\
                   & \qquad \quad  \forall \heapSat{n}{W}, \heap_f \ldotp \\
                   & \qquad \qquad (n,\reg\update{r_0}{c}\update{\pcreg}{\pc},\heap \uplus \heap_f) \in \observations(W) \}
\end{align*}
